---
title: PESKAS data report
date: "Last compiled on `r Sys.Date()`"
mainfont: Montserrat
geometry: "left=3cm,right=3cm,top=2cm,bottom=2cm"
output:
  bookdown::html_document2:
   toc: true
   toc_depth: 2
header-includes: 
  - \usepackage{float} 
  - \floatplacement{figure}{H}
  - \usepackage{leading}
  - \leading{16pt}
  - \definecolor{myblue}{RGB}{68,117,151}
  - \let\counterwithout\relax
  - \let\counterwithin\relax
  - \usepackage{chngcntr}
urlcolor: myblue
bibliography: references.bib
nocite: '@*'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = FALSE)
```

```{r, include=FALSE}
# libraries
library(ggplot2)
library(magrittr)
library(tidytext)

setwd("../..")
pars <- peskas.timor.data.pipeline::read_config()

# get data
public_files <-
  c("timor_aggregated", "timor_trips", "timor_catch", "timor_taxa_aggregated") %>%
  purrr::map(., ~ peskas.timor.data.pipeline::cloud_object_name(
    prefix = .x,
    version = "latest",
    extension = "rds",
    provider = pars$public_storage$google$key,
    options = pars$public_storage$google$options
  )) %>%
  do.call("rbind", .) %>%
  as.character() %>%
  unique() %>%
  purrr::walk(.,
    peskas.timor.data.pipeline::download_cloud_file,
    provider = pars$public_storage$google$key,
    options = pars$public_storage$google$options
  )

taxa_aggregated <- readRDS(list.files(pattern = "taxa_aggregated"))
aggregated <- readRDS(list.files(pattern = "timor_aggregated"))
trips <- readRDS(list.files(pattern = "timor_trips"))
catch <- readRDS(list.files(pattern = "timor_catch"))
metadata <- peskas.timor.data.pipeline::get_preprocessed_metadata(pars)
nutrient_table <- peskas.timor.data.pipeline::get_nutrients_table(pars)
estimates <- peskas.timor.data.pipeline::get_models(pars)

vessels_stats <-
  metadata$vessels_stats %>%
  dplyr::group_by(.data$reporting_region) %>%
  dplyr::summarise(n_boats = sum(.data$n_boats)) %>%
  dplyr::ungroup()

catch_types <- readRDS(list.files(pattern = "metadata"))$catch_types %>%
  dplyr::filter(!catch_name_en %in% c("Herring", "Unknown", "Surgeonfish")) %>% # remove duplicates
  dplyr::select(
    "catch_taxon" = interagency_code,
    "Taxonomic rank (family)" = catch_family,
    "Common name" = catch_name_en
  )

file.remove(c(
  public_files,
  list.files(pattern = "metadata"),
  list.files(pattern = "merged"),
  list.files(pattern = "rfish"),
  list.files(pattern = "model")
))

catch <-
  catch_types %>%
  dplyr::select(catch_taxon,
    comm_name = "Common name"
  ) %>%
  dplyr::right_join(catch, by = "catch_taxon") %>%
  dplyr::ungroup()

# palettes
year_palette <-
  rev(c("#bda639", "#1b5767", "#629a9b", "#c51f5d", "#92684d", "#9ECE9A"))
catch_use_palette <- rev(c("#9f8985", "#87bdbc", "#dbdbc9"))

# help functions
label_date <- function(x) {
  format(x, "%b") %>%
    stringr::str_replace("Jan", paste0("Jan\n", format(x, "%Y")))
}

# useful data
temp_range <- paste(zoo::as.yearmon(min(aggregated$month$date_bin_start, na.rm = TRUE)),
  zoo::as.yearmon(max(aggregated$month$date_bin_start, na.rm = TRUE)),
  sep = " - "
)

total_value <- sum(trips$landing_value, na.rm = TRUE)
total_weight <- sum(catch$weight, na.rm = TRUE)


RDI_Protein <- pars$metadata$nutrients$RDI$name$protein
RDI_VitaminA <- pars$metadata$nutrients$RDI$name$vitaminA
RDI_Calcium <- pars$metadata$nutrients$RDI$name$calcium
RDI_Selenium <- pars$metadata$nutrients$RDI$name$selenium
RDI_Zinc <- pars$metadata$nutrients$RDI$name$zinc
RDI_Iron <- pars$metadata$nutrients$RDI$name$iron
RDI_Omega <- pars$metadata$nutrients$RDI$name$omega3
```

------------------------------------------------------------------------

# Aim

This report is automatically generated in the last step of [Peskas' data pipeline](https://github.com/WorldFishCenter/peskas.timor.data.pipeline) and summarises the main statistics and insights related to small-scale fisheries in Timor during the period `r temp_range`. The report gives an overview of the Peskas' fleet and provide aggregated statistics and time series of the total revenue and total catch. The report provide also information on the catch composition, highlighting the most important fish groups in terms of overall stock.

\pagebreak

# Peskas fleet

```{r echo=FALSE, fig.height=4, fig.width=10, message=FALSE, warning=FALSE, out.height="100%",out.width="100%"}
gear_plot <-
  tidyr::tibble(
    gear_id = metadata$gear_types$gear_id,
    n = purrr::map_dbl(metadata$gear_types$boats, length)
  ) %>%
  dplyr::mutate(
    dummy_var = rep("dummycol", nrow(.)),
    total = sum(n),
    proportion = n / total * 100,
    proportion_label = dplyr::case_when(
      proportion < 5 ~ NA_real_,
      TRUE ~ proportion
    )
  )

gear_plot_dat <- list(
  top_gear = (gear_plot %>%
    dplyr::arrange(dplyr::desc(proportion)) %>%
    head(2) %>%
    magrittr::extract2("gear_id") %>%
    paste(collapse = " and ")),
  top_gear_n = round((gear_plot %>%
    dplyr::arrange(dplyr::desc(proportion_label)) %>%
    head(2) %>%
    magrittr::extract2("proportion") %>%
    sum()) - 1, 1)
)

vessel_plot <-
  trips %>%
  dplyr::group_by(vessel_type) %>%
  dplyr::count() %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    tot = sum(.data$n, na.rm = TRUE),
    prop = n / tot * 100,
    dummy_var = rep("dummycol", nrow(.))
  )

vessel_plot_dat <-
  vessel_plot %>%
  dplyr::filter(!is.na(vessel_type)) %>%
  dplyr::arrange(dplyr::desc(prop)) %>%
  dplyr::first()

gear_plot_caption <- paste0("The Peskas' fleet is composed of a total of 2334 boats, among these 451 are recorded.
More than ", gear_plot_dat$top_gear_n, "% are equipped with ", gear_plot_dat$top_gear, ". Most of these boats are ", vessel_plot_dat[1])

gear_plot <-
  gear_plot %>%
  ggplot(aes(x = dummy_var, y = n, fill = reorder(gear_id, n))) +
  geom_col(width = 5) +
  geom_text(aes(label = ifelse(is.na(proportion_label), "", paste0(round(proportion_label, 1), "%"))),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold",
    na.rm = TRUE
  ) +
  theme_minimal(15) +
  theme(
    legend.position = "top",
    panel.border = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.y = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.y = element_blank(),
    axis.ticks.x = element_blank(),
    plot.title = element_text(size = 18),
    plot.subtitle = element_text(size = 13, color = "darkslategrey")
  ) +
  labs(
    y = "", x = "", fill = "Gear type",
    title = "Boats gear type",
    subtitle = gear_plot_caption
  ) +
  scale_fill_brewer(type = "div", direction = 1) +
  coord_flip()


vessel_plot <-
  vessel_plot %>%
  ggplot(aes(x = dummy_var, y = n, fill = reorder(vessel_type, n))) +
  geom_col(width = 5) +
  geom_text(aes(label = ifelse(is.na(prop), "", paste0(round(prop, 0), "%"))),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold",
    na.rm = TRUE
  ) +
  theme_minimal(15) +
  theme(
    legend.position = "right",
    panel.border = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.y = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.y = element_blank(),
    axis.ticks.x = element_blank(),
    plot.title = element_text(size = 18),
    plot.subtitle = element_text(size = 13, color = "darkslategrey")
  ) +
  labs(
    y = "", x = "", fill = "Vessel type"
  ) +
  scale_fill_manual(values = rev(c("#49566e", "#fad591"))) +
  coord_polar("y", start = 0)

cowplot::plot_grid(gear_plot, vessel_plot, ncol = 2, axis = "t", align = "hv", rel_widths = c(4, 2))
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=3, fig.width=6,out.height="100%",out.width="100%"}
metadata$boats %>%
  dplyr::select(.data$boat_length, .data$boat_engine_power) %>%
  tidyr::pivot_longer(cols = tidyr::everything()) %>%
  ggplot() +
  theme_minimal(10) +
  facet_grid(. ~ name,
    scales = "free",
    labeller = as_labeller(c(
      boat_engine_power = "Boat horspower (hp)",
      boat_length = "Boat length (m)"
    ))
  ) +
  geom_histogram(mapping = aes(x = value), bins = 30, binwidth = 0.5, color = "#447597", fill = "#447597", alpha = 0.3) +
  theme(
    text = element_text(family = "Helvetica"),
    plot.subtitle = element_text(size = 9, color = "darkslategrey")
  ) +
  labs(
    title = "Boat properties",
    x = "",
    y = "Frequency",
    subtitle = "Most of the boats are equipped with a 15-hp motor and measure between 3 and 7 meters.\nVery few of them are longer than 10 meters."
  )
```

\pagebreak

# National indicators


## Number of trips

```{r echo=FALSE, fig.height=4, fig.width=8, message=FALSE, warning=FALSE}
estimates$national$aggregated %>%
  dplyr::mutate(n = n_landings_per_boat * sum(metadata$registered_boats$n_boats)) %>%
  ggplot(aes(landing_period, n)) +
  geom_line(color = "#447597") +
  geom_point(color = "#447597") +
  # geom_area(fill="#447597",alpha=0.15)+
  stat_smooth(method = "loess", color = "#976644", alpha = 0.1, size = 0.5) +
  labs(
    x = "Date", y = "Fishing trips"
  ) +
  scale_x_date(
    date_breaks = "4 month", minor_breaks = NULL, labels = label_date,
    limits = c(as.Date("2018-01-01"), Sys.Date() - 31)
  ) +
  scale_y_continuous(labels = scales::comma) +
  theme_minimal(14) +
  theme(
    panel.grid.minor.x = element_blank(),
    text = element_text(family = "Helvetica"),
    plot.title = element_text(size = 18),
    plot.subtitle = element_text(size = 12, color = "darkslategrey")
  )
```

## Fishing effort

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=4, fig.width=8}
effort_dat <-
  trips %>%
  dplyr::mutate(month_date = lubridate::floor_date(.data$landing_date,
    "month",
    week_start = 7
  )) %>%
  dplyr::select(month_date, landing_survey_trip_duration) %>%
  dplyr::group_by(month_date) %>%
  dplyr::summarise(
    mean = mean(landing_survey_trip_duration, na.rm = TRUE),
    sd = sd(landing_survey_trip_duration, na.rm = TRUE),
    n = dplyr::n()
  )

effort_caption <- paste0(
  "The average trip duration of Peskas' boats is of ",
  round(mean(effort_dat$mean, na.rm = TRUE), 1), " ± ", round(mean(effort_dat$sd, na.rm = TRUE), 1),
  " hours. As there are\non average ", round(mean(effort_dat$n, na.rm = TRUE), 0),
  " trips each month, the monthly fishing effort is about of ",
  round(mean(effort_dat$n, na.rm = TRUE), 0) * round(mean(effort_dat$mean, na.rm = TRUE), 1),
  " hours."
)
trips %>%
  dplyr::mutate(month_date = lubridate::floor_date(.data$landing_date,
    "month",
    week_start = 7
  )) %>%
  dplyr::select(month_date, landing_survey_trip_duration) %>%
  dplyr::group_by(month_date) %>%
  dplyr::summarise(
    mean = mean(landing_survey_trip_duration, na.rm = TRUE),
    sd = sd(landing_survey_trip_duration, na.rm = TRUE),
    n = dplyr::n()
  ) %>%
  dplyr::mutate(
    se = sd / sqrt(n),
    ic = se * qt((1 - 0.05) / 2 + .5, n - 1)
  ) %>%
  ggplot(aes(as.Date(month_date), mean)) +
  geom_line(color = "#447597") +
  geom_point(color = "#447597") +
  geom_area(fill = "#447597", alpha = 0.15) +
  geom_pointrange(
    aes(ymin = mean - ic, ymax = mean + ic),
    position = position_dodge(0.3),
    color = "#447597"
  ) +
  theme_minimal(14) +
  scale_y_continuous(labels = scales::comma) +
  scale_x_date(
    date_breaks = "4 month", minor_breaks = NULL, labels = label_date,
    limits = c(as.Date("2018-01-01"), Sys.Date() - 31)
  ) +
  theme(
    panel.grid.minor.x = element_blank(),
    text = element_text(family = "Helvetica"),
    plot.title = element_text(size = 18),
    plot.subtitle = element_text(size = 12, color = "darkslategrey")
  ) +
  labs(
    x = "Date", y = "Fishing effort (hours)",
    title = "Interannual distribution of fishing effort",
    subtitle = effort_caption
  )
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=3, fig.width=4}
trips %>%
  dplyr::filter(landing_survey_trip_duration > 0 & landing_survey_trip_duration != "NA") %>%
  dplyr::mutate(
    month_date = lubridate::floor_date(.data$landing_date,
      "month",
      week_start = 7
    ),
    year = lubridate::year(.data$landing_date)
  ) %>%
  dplyr::select(year, month_date, landing_survey_trip_duration) %>%
  dplyr::group_by(year, month_date) %>%
  dplyr::summarise(
    monthly_effort = sum(landing_survey_trip_duration, na.rm = TRUE),
    trips = dplyr::n()
  ) %>%
  na.omit() %>%
  ggplot(aes(trips, monthly_effort)) +
  geom_point(aes(color = as.factor(year)), alpha = 0.6) +
  stat_smooth(method = "lm", alpha = 0, color = "firebrick", size = 0.5) +
  theme_minimal(11) +
  theme(
    text = element_text(family = "Helvetica"),
    plot.title = element_text(size = 18),
    plot.subtitle = element_text(size = 9, color = "darkslategrey")
  ) +
  labs(
    x = "Number of trips", y = "Fishing effort (hours)",
    color = "Year",
    subtitle = "Except for 2019, where there appears to be a greater fishing\neffort in proportion to the number of fishing trips, the\nrelationship between the two is stable throughout\nPeskas' period of activity."
  ) +
  scale_color_manual(values = year_palette)
```

\pagebreak

## Catch volume

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=4, fig.width=8}
estimates$national$aggregated %>%
  ggplot(aes(landing_period, catch / 1000)) +
  geom_line(color = "#447597") +
  geom_point(color = "#447597") +
  geom_area(fill = "#447597", alpha = 0.15) +
  stat_smooth(method = "loess", color = "#976644", alpha = 0.1, size = 0.5) +
  labs(
    x = "Date", y = "Catch volume (tons)"
  ) +
  scale_x_date(
    date_breaks = "4 month", minor_breaks = NULL, labels = label_date,
    limits = c(as.Date("2018-01-01"), Sys.Date() - 31)
  ) +
  scale_y_continuous(labels = scales::comma) +
  theme_minimal(14) +
  theme(
    panel.grid.minor.x = element_blank(),
    text = element_text(family = "Helvetica"),
    plot.title = element_text(size = 18),
    plot.subtitle = element_text(size = 12, color = "darkslategrey")
  )
```

## Catch revenue

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=4, fig.width=8}
estimates$national$aggregated %>%
  ggplot(aes(landing_period, revenue)) +
  geom_line(color = "#447597") +
  geom_point(color = "#447597") +
  geom_area(fill = "#447597", alpha = 0.15) +
  stat_smooth(method = "loess", color = "#976644", alpha = 0.1, size = 0.5) +
  labs(
    x = "Date", y = "Catch revenue (USD)"
  ) +
  scale_x_date(
    date_breaks = "4 month", minor_breaks = NULL, labels = label_date,
    limits = c(as.Date("2018-01-01"), Sys.Date() - 31)
  ) +
  scale_y_continuous(labels = scales::comma) +
  theme_minimal(14) +
  theme(
    panel.grid.minor.x = element_blank(),
    text = element_text(family = "Helvetica"),
    plot.title = element_text(size = 18),
    plot.subtitle = element_text(size = 12, color = "darkslategrey")
  )
```

```{r, echo=FALSE, warning=FALSE, fig.height=4, fig.width=7}
aggregated$month %>%
  dplyr::mutate(
    month = lubridate::month(date_bin_start, label = TRUE),
    year = lubridate::year(date_bin_start)
  ) %>%
  dplyr::filter(!is.na(date_bin_start) & year != 2017) %>%
  dplyr::select(year, month, date_bin_start, revenue) %>%
  ggplot() +
  geom_line(mapping = aes(x = as.factor(month), y = revenue, color = as.factor(year), group = as.factor(year))) +
  geom_point(mapping = aes(x = as.factor(month), y = revenue, color = as.factor(year))) +
  labs(
    x = "", y = "total revenue (USD)", color = "year",
    title = "Seasonal total revenue",
    subtitle = "Except for 2019, the total revenue is seasonal, showing\nthe highest during the dry season."
  ) +
  scale_color_manual(values = year_palette) +
  scale_y_continuous(labels = scales::comma) +
  coord_polar() +
  theme_minimal(12) +
  theme(
    axis.ticks.y = element_line(colour = "black"),
    text = element_text(family = "Helvetica"),
    plot.title = element_text(size = 15),
    plot.subtitle = element_text(size = 10.5, color = "darkslategrey")
  )
```

\pagebreak

## Market value

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=4, fig.width=8}
estimates$national$aggregated %>%
  ggplot(aes(landing_period, price_kg)) +
  geom_line(color = "#447597") +
  geom_point(color = "#447597") +
  stat_smooth(method = "loess", color = "#976644", alpha = 0.1, size = 0.5) +
  labs(
    x = "Date", y = "Price per Kg (USD)"
  ) +
  scale_x_date(
    date_breaks = "4 month", minor_breaks = NULL, labels = label_date,
    limits = c(as.Date("2018-01-01"), Sys.Date() - 31)
  ) +
  scale_y_continuous(labels = scales::comma) +
  theme_minimal(14) +
  theme(
    panel.grid.minor.x = element_blank(),
    text = element_text(family = "Helvetica"),
    plot.title = element_text(size = 18),
    plot.subtitle = element_text(size = 12, color = "darkslategrey")
  )
```

\pagebreak

## Catch usage

```{r, echo=FALSE, warning=FALSE, fig.height=7, fig.width=4.5,out.height="100%",out.width="100%"}
rank_catch <-
  catch %>%
  dplyr::filter(individuals != 0 & comm_name != "NA") %>%
  dplyr::count(comm_name, catch_purpose) %>%
  ggplot() +
  geom_col(mapping = aes(x = reorder(comm_name, n), y = n, fill = catch_purpose)) +
  theme_minimal(13) +
  theme(text = element_text(family = "Helvetica")) +
  theme(legend.position = "") +
  scale_fill_manual(values = catch_use_palette) +
  scale_y_continuous(labels = scales::comma) +
  labs(y = "number of catches", x = "", fill = "") +
  coord_flip()

tot_catch <-
  catch %>%
  dplyr::filter(individuals != 0) %>%
  dplyr::count(catch_purpose) %>%
  dplyr::mutate(
    dummy_var = rep("dummycol", nrow(.)),
    total_catches = sum(n),
    proportion = n / total_catches * 100
  ) %>%
  ggplot(aes(x = dummy_var, y = n, fill = catch_purpose)) +
  geom_col(width = 5) +
  geom_text(aes(label = paste0(round(proportion, 1), "%")),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  ) +
  theme_minimal(13) +
  theme(
    legend.position = "top",
    panel.border = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.y = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.y = element_blank(),
    axis.ticks.x = element_blank(),
    plot.title = element_text(size = 18),
    plot.subtitle = element_text(size = 12, color = "darkslategrey")
  ) +
  labs(
    y = "", x = "", fill = "Catch usage",
    title = "Catches final usage",
    subtitle = "Sardines and pilchards are by far the most fished species followed by scads\nand emperor fishes. Overall, more than 70% of the catch is doomed for sale,\nexcept for some groups caught for sustenance as unicornfish and soldierfish."
  ) +
  scale_fill_manual(values = catch_use_palette) +
  coord_flip()

cowplot::plot_grid(tot_catch,
  rank_catch,
  ncol = 1,
  rel_heights = c(2.5, 9),
  align = "v"
)
```

\pagebreak

```{r, echo=FALSE, warning=FALSE,message=FALSE, fig.height=5, fig.width=8}
dplyr::left_join(catch, trips, by = "trip_id") %>%
  dplyr::filter(individuals != 0) %>%
  dplyr::mutate(landing_date_month = lubridate::floor_date(landing_date, unit = "month")) %>%
  dplyr::group_by(landing_date_month) %>%
  dplyr::count(catch_purpose) %>%
  dplyr::mutate(
    tot = sum(n, na.rm = TRUE),
    usage_proportion = n / tot * 100
  ) %>%
  ggplot(aes(landing_date_month, usage_proportion, group = catch_purpose, color = catch_purpose)) +
  geom_line() +
  geom_point() +
  labs(
    x = "month", y = "Usage proportion",
    color = "usage proportion",
    title = "Time series of catches final usage",
    subtitle = "Since 2019 catches sale is constantly increasing relatively to other usages."
  ) +
  scale_x_date(
    date_breaks = "3 month", minor_breaks = NULL, labels = label_date,
    limits = c(as.Date("2019-01-01"), Sys.Date() - 31)
  ) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  scale_color_manual(values = catch_use_palette) +
  theme_minimal(15) +
  theme(
    text = element_text(family = "Helvetica"),
    legend.position = "top",
    legend.title = element_blank(),
    plot.title = element_text(size = 18),
    plot.subtitle = element_text(size = 12, color = "darkslategrey")
  )
```

\pagebreak

## Stock composition

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5, fig.width=5,out.height="100%",out.width="100%"}
trips %>%
  tidyr::unnest(landing_catch) %>%
  tidyr::unnest(length_frequency) %>%
  dplyr::select(trip_id, catch_taxon, individuals, weight) %>%
  dplyr::filter(individuals > 0) %>%
  dplyr::left_join(catch_types, by = "catch_taxon") %>%
  dplyr::select(-`Taxonomic rank (family)`) %>%
  dplyr::rename(comm_name = `Common name`) %>%
  dplyr::mutate(total_weight = sum(weight, na.rm = T)) %>%
  dplyr::group_by(comm_name) %>%
  dplyr::summarise(
    total_weight = dplyr::first(total_weight),
    aggregated_weight = sum(weight, na.rm = TRUE)
  ) %>%
  dplyr::mutate(weight_proportion = aggregated_weight / total_weight * 100) %>%
  dplyr::arrange(dplyr::desc(weight_proportion)) %>%
  dplyr::mutate(cumulative = cumsum(weight_proportion)) %>%
  dplyr::arrange(weight_proportion) %>%
  dplyr::mutate(comm_name = factor(comm_name, levels = .$comm_name)) %>%
  dplyr::arrange(cumulative) %>%
  ggplot(aes(weight_proportion, comm_name)) +
  geom_segment(aes(yend = comm_name), xend = 0, colour = "#525B76") +
  geom_point(size = 2.5, color = "#525B76") +
  theme_minimal(13) +
  scale_x_continuous(labels = scales::percent_format(scale = 1)) +
  # scale_color_manual(labels = c("Economic value", "Weight"), values = c("#669966", "#996699")) +
  labs(
    x = "Overall live weight proportion", y = "",
    title = "Overall species' stock proportion"
  ) +
  theme(
    panel.grid.minor.x = element_blank(),
    legend.position = "top",
    legend.title = element_blank(),
    text = element_text(family = "Helvetica"),
    plot.title = element_text(size = 19),
    plot.subtitle = element_text(size = 14, color = "darkslategrey")
  )
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5.5, fig.width=6.5,out.height="100%",out.width="100%"}
estimates$national$taxa %>%
  dplyr::rename(catch_taxon = grouped_taxa) %>%
  dplyr::left_join(catch_types, by = "catch_taxon") %>%
  dplyr::rename(comm_name = `Common name`) %>%
  dplyr::filter(catch_taxon %in% c("CLP", "TUN", "CJX", "SDX")) %>%
  dplyr::select(comm_name, landing_period, catch) %>%
  dplyr::group_by(landing_period, comm_name) %>%
  dplyr::summarise(catch = sum(catch, na.rm = TRUE)) %>%
  dplyr::mutate(comm_name = dplyr::case_when(
    comm_name == "Sardines/pilchards" ~ "Sardines",
    comm_name == "Tuna/Bonito/Other Mackerel" ~ "Tuna/Bonito",
    TRUE ~ comm_name
  )) %>%
  ggplot(aes(x = landing_period, y = catch / 1000)) +
  facet_grid(comm_name ~ ., scales = "free_y") +
  geom_line(aes(color = comm_name), show.legend = FALSE) +
  geom_area(aes(fill = comm_name), alpha = 0.5) +
  scale_x_date(
    date_breaks = "4 month", minor_breaks = NULL, labels = label_date,
    limits = c(as.Date("2018-01-01"), Sys.Date() - 31)
  ) +
  scale_y_continuous(labels = scales::comma, limits = c(0, NA)) +
  scale_color_manual(values = c("#50514f", "#cbd4c2", "#07004d", "#247ba0")) +
  scale_fill_manual(values = c("#50514f", "#cbd4c2", "#07004d", "#247ba0")) +
  theme_minimal(13) +
  theme(
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    text = element_text(family = "Helvetica"),
    legend.position = "bottom",
    plot.title = element_text(size = 18),
    plot.subtitle = element_text(size = 13, color = "darkslategrey")
  ) +
  labs(
    x = "Date", y = "Tonnes live catch",
    color = "Fish group",
    fill = "",
    title = "Interannual species distribution",
    subtitle = "Fishing of the most important species remained mostly stable, except for a\nconsiderable increase of fusiliers and to a lesser extent of Tuna-like species."
  )
```

\pagebreak

## Gender composition

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5, fig.width=8}
trips %>%
  dplyr::select(landing_date, tidyselect::starts_with("fisher")) %>%
  tidyr::pivot_longer(cols = -landing_date) %>%
  dplyr::mutate(landing_date = lubridate::floor_date(.data$landing_date, unit = "month")) %>%
  dplyr::group_by(landing_date, name) %>%
  dplyr::summarise(value = sum(value, na.rm = TRUE)) %>%
  ggplot(aes(landing_date, value,
    fill =
      factor(name, levels = c("fisher_number_child", "fisher_number_woman", "fisher_number_man"))
  )) +
  geom_col(alpha = 0.6) +
  labs(
    x = "Date", y = "Number of fishers",
    title = "Fishers gender",
    subtitle = "Monthly number of fishers in Timor based on collected surveys, male adult fishers\nare by far the most representative.",
    fill = ""
  ) +
  scale_x_date(
    date_breaks = "3 month", minor_breaks = NULL, labels = label_date,
    limits = c(as.Date("2018-07-01"), Sys.Date() - 31)
  ) +
  theme_minimal(15) +
  theme(
    text = element_text(family = "Helvetica"),
    plot.title = element_text(size = 18),
    plot.subtitle = element_text(size = 13, color = "darkslategrey"),
    legend.position = "bottom",
    legend.title = element_text()
  ) +
  scale_fill_manual(
    labels = c("child", "female", "male"),
    values = c("#383002", "#bdb37b", "#0b9984")
  )
```

\pagebreak

# Municipal indicators

Estimates of municipal data were interpolated in order to fill data gaps in the time series. Interpolated values in the following plots are represented by red points.

## Number of trips

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=12, fig.width=10}
estimates$municipal %>%
  purrr::map(~ purrr::keep(.x, stringr::str_detect(
    names(.x), stringr::fixed("aggregated")
  ))) %>%
  purrr::flatten() %>%
  purrr::set_names(names(estimates$municipal)) %>%
  dplyr::bind_rows(.id = "reporting_region") %>%
  dplyr::mutate(n = n_landings_per_boat * n_boats) %>%
  ggplot(aes(landing_period, n)) +
  facet_wrap(~reporting_region, ncol = 2, scales = "free") +
  geom_line(color = "#447597") +
  geom_point(aes(color = is_imputed)) +
  geom_area(fill = "#447597", alpha = 0.15) +
  stat_smooth(method = "loess", color = "#976644", alpha = 0.1, size = 0.5) +
  labs(
    x = "Date", y = "Fishing trips"
  ) +
  scale_x_date(
    date_breaks = "4 month", minor_breaks = NULL, labels = label_date,
    limits = c(as.Date("2018-01-01"), Sys.Date() - 31)
  ) +
  scale_y_continuous(labels = scales::comma) +
  scale_color_manual(values = c("#505050", "#d23f67")) +
  theme_minimal(13) +
  theme(
    panel.grid.minor.x = element_blank(),
    text = element_text(family = "Helvetica"),
    plot.title = element_text(size = 18),
    plot.subtitle = element_text(size = 12, color = "darkslategrey")
  ) +
  guides(color = "none")
```

\pagebreak

## Catch volume

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=12, fig.width=10}
estimates$municipal %>%
  purrr::map(~ purrr::keep(.x, stringr::str_detect(
    names(.x), stringr::fixed("aggregated")
  ))) %>%
  purrr::flatten() %>%
  purrr::set_names(names(estimates$municipal)) %>%
  dplyr::bind_rows(.id = "reporting_region") %>%
  dplyr::left_join(vessels_stats, by = "reporting_region") %>%
  ggplot(aes(landing_period, catch / 1000)) +
  facet_wrap(~reporting_region, ncol = 2, scales = "free") +
  geom_line(color = "#447597") +
  geom_point(aes(color = is_imputed)) +
  geom_area(fill = "#447597", alpha = 0.15) +
  stat_smooth(method = "loess", color = "#976644", alpha = 0.1, size = 0.5) +
  labs(x = "Date", y = "Catch volume (tons)") +
  scale_x_date(
    date_breaks = "4 month", minor_breaks = NULL, labels = label_date,
    limits = c(as.Date("2018-01-01"), Sys.Date() - 31)
  ) +
  scale_y_continuous(labels = scales::comma) +
  scale_color_manual(values = c("#505050", "#d23f67")) +
  theme_minimal(13) +
  theme(
    panel.grid.minor.x = element_blank(),
    text = element_text(family = "Helvetica"),
    plot.title = element_text(size = 18),
    plot.subtitle = element_text(size = 12, color = "darkslategrey")
  ) +
  guides(color = "none")
```

\pagebreak

## Catch revenue

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=12, fig.width=10}
estimates$municipal %>%
  purrr::map(~ purrr::keep(.x, stringr::str_detect(
    names(.x), stringr::fixed("aggregated")
  ))) %>%
  purrr::flatten() %>%
  purrr::set_names(names(estimates$municipal)) %>%
  dplyr::bind_rows(.id = "reporting_region") %>%
  dplyr::left_join(vessels_stats, by = "reporting_region") %>%
  ggplot(aes(landing_period, revenue)) +
  facet_wrap(~reporting_region, ncol = 2, scales = "free") +
  geom_line(color = "#447597") +
  geom_point(aes(color = is_imputed)) +
  geom_area(fill = "#447597", alpha = 0.15) +
  stat_smooth(method = "loess", color = "#976644", alpha = 0.1, size = 0.5) +
  labs(x = "Date", y = "Catch revenue (USD)") +
  scale_x_date(
    date_breaks = "4 month", minor_breaks = NULL, labels = label_date,
    limits = c(as.Date("2018-01-01"), Sys.Date() - 31)
  ) +
  scale_y_continuous(labels = scales::comma) +
  scale_color_manual(values = c("#505050", "#d23f67")) +
  theme_minimal(13) +
  theme(
    panel.grid.minor.x = element_blank(),
    text = element_text(family = "Helvetica"),
    plot.title = element_text(size = 18),
    plot.subtitle = element_text(size = 12, color = "darkslategrey")
  ) +
  guides(color = "none")
```

\pagebreak

## Market value

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=12, fig.width=10}
estimates$municipal %>%
  purrr::map(~ purrr::keep(.x, stringr::str_detect(
    names(.x), stringr::fixed("aggregated")
  ))) %>%
  purrr::flatten() %>%
  purrr::set_names(names(estimates$municipal)) %>%
  dplyr::bind_rows(.id = "reporting_region") %>%
  dplyr::left_join(vessels_stats, by = "reporting_region") %>%
  ggplot(aes(landing_period, price_kg)) +
  facet_wrap(~reporting_region, ncol = 2, scales = "free") +
  geom_line(color = "#447597") +
  geom_point(aes(color = is_imputed)) +
  geom_area(fill = "#447597", alpha = 0.15) +
  stat_smooth(method = "loess", color = "#976644", alpha = 0.1, size = 0.5) +
  labs(x = "Date", y = "Price per Kg (USD)") +
  scale_x_date(
    date_breaks = "4 month", minor_breaks = NULL, labels = label_date,
    limits = c(as.Date("2018-01-01"), Sys.Date() - 31)
  ) +
  scale_y_continuous(labels = scales::comma) +
  scale_color_manual(values = c("#505050", "#d23f67")) +
  theme_minimal(13) +
  theme(
    panel.grid.minor.x = element_blank(),
    text = element_text(family = "Helvetica"),
    plot.title = element_text(size = 18),
    plot.subtitle = element_text(size = 12, color = "darkslategrey")
  ) +
  guides(color = "none")
```

\pagebreak

## Catch usage 

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=6, fig.width=8}
catch_usage <-
  catch %>%
  dplyr::group_by(trip_id) %>%
  dplyr::summarise(catch_purpose = dplyr::first(.data$catch_purpose)) %>%
  dplyr::ungroup()
trips_usage <-
  trips %>%
  dplyr::filter(!is.na(.data$tracker_trip_start)) %>%
  dplyr::group_by(trip_id) %>%
  dplyr::summarise(reporting_region = dplyr::first(.data$reporting_region)) %>%
  dplyr::ungroup()

region_usage <-
  dplyr::full_join(trips_usage, catch_usage, by = "trip_id") %>%
  dplyr::filter(!is.na(.data$reporting_region) & !is.na(.data$catch_purpose)) %>%
  dplyr::group_by(.data$reporting_region) %>%
  dplyr::count(.data$catch_purpose) %>%
  dplyr::group_by(.data$reporting_region) %>%
  dplyr::mutate(tot_obs = sum(n)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(obs_perc = .data$n / .data$tot_obs * 100)


region_usage %>%
  ggplot() +
  # geom_col(mapping = aes(x = reorder(reporting_region, obs_perc), y = obs_perc, fill = catch_purpose)) +
  geom_col(mapping = aes(x = reporting_region, y = obs_perc, fill = catch_purpose)) +
  theme_minimal(15) +
  theme(text = element_text(family = "Helvetica")) +
  theme(legend.position = "right") +
  scale_fill_manual(values = catch_use_palette) +
  scale_y_continuous(labels = scales::comma, expand = c(0, 0)) +
  labs(y = "Catch usage (%)", x = "", fill = "") +
  coord_flip()
```

\pagebreak


## Stock composition

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5, fig.width=5,out.height="100%",out.width="100%"}
p1 <-
  dplyr::left_join(catch, trips, by = "trip_id") %>%
  dplyr::filter(individuals > 0) %>%
  dplyr::mutate(
    catch_taxon = dplyr::case_when(
      catch_taxon %in% pars$models$modelled_taxa ~ catch_taxon,
      TRUE ~ "MZZ"
    ),
    comm_name = dplyr::case_when(
      catch_taxon == "MZZ" ~ "Other",
      TRUE ~ comm_name
    )
  ) %>%
  dplyr::select(reporting_region, comm_name, catch_taxon, weight) %>%
  dplyr::group_by(reporting_region, comm_name, catch_taxon) %>%
  dplyr::summarise(weight = sum(weight, na.rm = TRUE)) %>%
  dplyr::group_by(reporting_region) %>%
  dplyr::mutate(total_weight = sum(weight, na.rm = TRUE)) %>%
  dplyr::filter(catch_taxon %in% pars$models$modelled_taxa) %>%
  dplyr::filter(!is.na(reporting_region)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(reporting_region = forcats::fct_reorder(reporting_region, total_weight)) %>%
  ggplot(aes(weight, reporting_region, fill = comm_name)) +
  geom_col(position = "fill", alpha = 0.75) +
  scale_x_continuous(
    labels = scales::percent,
    expand = c(0, 0)
  ) +
  theme_minimal(13) +
  labs(
    x = "Overall catch composition",
    y = "",
    title = ""
  ) +
  scale_fill_viridis_d() +
  theme(
    panel.grid.minor.x = element_blank(),
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.text = element_text(size = 7.5),
    legend.key.size = unit(1, "line"),
    text = element_text(family = "Helvetica"),
    plot.title = element_text(size = 19),
    plot.subtitle = element_text(size = 14, color = "darkslategrey")
  )

leg <- ggpubr::get_legend(p1)
leg <- ggpubr::as_ggplot(leg)

p2 <-
  dplyr::left_join(catch, trips, by = "trip_id") %>%
  dplyr::filter(individuals > 0) %>%
  dplyr::select(reporting_region, comm_name, weight) %>%
  dplyr::group_by(reporting_region, comm_name) %>%
  dplyr::summarise(weight = sum(weight, na.rm = TRUE)) %>%
  dplyr::arrange(dplyr::desc(weight)) %>%
  dplyr::top_n(5) %>%
  dplyr::filter(!is.na(reporting_region)) %>%
  dplyr::mutate(total_weight = sum(weight, na.rm = TRUE) / 1000000) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(reporting_region = forcats::fct_reorder(reporting_region, total_weight)) %>%
  ggplot(aes(total_weight, reporting_region)) +
  geom_point(size = 2.5, color = "#525B76") +
  geom_segment(aes(yend = reporting_region), xend = 0, colour = "#525B76") +
  theme_minimal(15) +
  labs(
    x = "Aggregated weight (tons)",
    y = ""
  ) +
  theme(
    panel.grid.minor.x = element_blank(),
    legend.position = "top",
    legend.title = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    text = element_text(family = "Helvetica"),
    plot.title = element_text(size = 19),
    plot.subtitle = element_text(size = 14, color = "darkslategrey")
  )


cow1 <-
  cowplot::plot_grid(p1 + theme(legend.position = "none"),
    p2 + theme(plot.margin = unit(c(0, 0, 0, -.75), "cm")),
    ncol = 2,
    nrow = 1,
    rel_widths = c(2, 1),
    rel_heights = c(3, 0.75),
    align = "h"
  )

p1
# cowplot::plot_grid(cow1,
#                   leg,
#                   nrow=2,
#                   rel_heights = c(3, 0.75))
```

\pagebreak

## Interannual fish groups composition

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=10, fig.width=9,out.height="100%",out.width="100%"}
municipal_taxa <-
  estimates$municipal %>%
  purrr::map(~ purrr::keep(.x, stringr::str_detect(
    names(.x), stringr::fixed("taxa")
  ))) %>%
  purrr::flatten() %>%
  purrr::set_names(names(estimates$municipal)) %>%
  dplyr::bind_rows(.id = "region") %>%
  dplyr::rename(date_bin_start = .data$landing_period) %>%
  dplyr::select(-c(.data$period, .data$month))

municipal_taxa %>%
  dplyr::select(.data$region, .data$date_bin_start, .data$grouped_taxa, .data$catch) %>%
  dplyr::rename(catch_taxon = .data$grouped_taxa) %>%
  dplyr::left_join(catch_types, by = "catch_taxon") %>%
  dplyr::rename(comm_name = `Common name`) %>%
  ggplot(aes(date_bin_start, catch / 1000, fill = comm_name)) +
  facet_wrap(. ~ region, scales = "free", ncol = 2) +
  geom_col(alpha = 0.7) +
  theme_minimal(13) +
  theme(text = element_text(family = "Helvetica")) +
  scale_fill_viridis_d() +
  theme(legend.position = "bottom") +
  scale_x_date(expand = c(0, 0)) +
  labs(x = "", y = "Catch (tons)", fill = "")
```

\pagebreak


# Boat tracking

Boat movements are tracked by [Pelagic Data System](https://www.pelagicdata.com/) tracking system, and a proprietary algorithm is used to determine when a trip occurs. Tracks are recorded by GPS devices mounted on the boats. The heatmap refer to the boats' movements tracked along the Timor coast with a grid resolution of 10 x 10 meters. The tracks are filtered for outliers and some potential algorithm errors. Specifically, we do not take into account geo-referenced tracks characterized by large anomalies in the quality of the tracking signal, the speed of the boats, and the distance and time travelled.



```{r, echo=FALSE, message=FALSE, warning=FALSE}
 knitr::include_graphics(peskas.timor.data.pipeline::get_tracks_map(pars))
#htmltools::includeHTML("https://github.com/WorldFishCenter/peskas.timor.portal/raw/main/inst/app/www/kepler_pds_map.html")
```

\pagebreak

# Gear type usage

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=6, fig.width=11}
gear_prop_dat <-
  trips %>%
  dplyr::select(landing_date, gear_type, landing_value) %>%
  dplyr::filter(gear_type != "NA", landing_value > 0) %>%
  dplyr::mutate(month_date = lubridate::floor_date(.data$landing_date,
    "month",
    week_start = 7
  )) %>%
  dplyr::group_by(gear_type) %>%
  dplyr::count() %>%
  dplyr::arrange(dplyr::desc(n))

gear_caption <-
  paste0("Gill nets nets constitute more than 50% of the catch on a monthly scale, and with", gear_prop_dat[1, 2], "is by far the most used\ngear type. Following, ", paste(gear_prop_dat[2, 1], gear_prop_dat[3, 1], gear_prop_dat[4, 1], sep = ", "), " are the most used with ", paste(gear_prop_dat[2, 2], gear_prop_dat[3, 2], gear_prop_dat[4, 2], sep = ", "), " trips respectively.\nExcept before 2020 when the use of long lines was marginal, the relative usage of different gear types\nwas comparable along the time series.")

trips %>%
  dplyr::select(landing_date, gear_type, landing_value) %>%
  dplyr::filter(gear_type != "NA", landing_value > 0) %>%
  dplyr::mutate(month_date = lubridate::floor_date(.data$landing_date,
    "month",
    week_start = 7
  )) %>%
  dplyr::group_by(month_date, gear_type) %>%
  dplyr::count(gear_type) %>%
  ggplot(aes(x = as.Date(month_date), y = n, fill = gear_type)) +
  geom_col(position = "fill") +
  scale_fill_brewer(type = "div", direction = 1) +
  theme_minimal(19) +
  scale_y_continuous(labels = scales::percent) +
  scale_x_date(
    date_breaks = "4 month", minor_breaks = NULL, labels = label_date,
    limits = c(as.Date("2018-01-01"), Sys.Date() - 31)
  ) +
  theme(
    text = element_text(family = "Helvetica"),
    plot.title = element_text(size = 20),
    plot.subtitle = element_text(size = 14, color = "darkslategrey")
  ) +
  labs(
    fill = "Gear type", x = "Date", y = "Proportion of catches",
    title = "Proportion of catches by gear type",
    subtitle = gear_caption
  )
```

\pagebreak

# Catch diversity

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=4, fig.width=8}
dplyr::left_join(catch, trips, by = "trip_id") %>%
  dplyr::filter(individuals > 0 & landing_n_taxa > 0) %>%
  dplyr::mutate(landing_date_month = lubridate::floor_date(landing_date, unit = "month")) %>%
  dplyr::select(landing_date_month, landing_n_taxa) %>%
  dplyr::group_by(landing_date_month) %>%
  dplyr::summarise(
    mean = mean(landing_n_taxa),
    sd = sd(landing_n_taxa),
    n = dplyr::n()
  ) %>%
  dplyr::mutate(
    se = sd / sqrt(n),
    ic = se * qt((1 - 0.05) / 2 + .5, n - 1),
    month = lubridate::month(landing_date_month, label = TRUE),
    year = lubridate::year(landing_date_month)
  ) %>%
  ggplot(aes(x = landing_date_month, y = mean)) +
  geom_line(color = "#447597") +
  geom_point(color = "#447597") +
  geom_pointrange(
    aes(ymin = mean - ic, ymax = mean + ic),
    position = position_dodge(0.3),
    color = "#447597"
  ) +
  stat_smooth(method = "loess", color = "#976644", alpha = 0.1) +
  labs(
    x = "month", y = "Catch diversity (number of taxa)",
    title = "Interannual catches diversity"
  ) +
  scale_x_date(
    date_breaks = "3 month", minor_breaks = NULL, labels = label_date,
    limits = c(as.Date("2019-01-01"), Sys.Date() - 31)
  ) +
  theme_minimal(14) +
  theme(
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    text = element_text(family = "Helvetica"),
    legend.position = "bottom",
    plot.title = element_text(size = 18),
    plot.subtitle = element_text(size = 13, color = "darkslategrey")
  )
```

\pagebreak


# Nutritional properties

The nutritional values for each catch were obtained by integrating the weight estimates for each fish-group retrieved from [FishBase](https://www.fishbase.se/search.php) with modelled concentrations of seven nutrients [@hicks2019] foundable in [FishBase Nutrient Research Tool](https://www.fishbase.se/Nutrients/NutrientSearch.php) and in the public repository associated to the paper on [GitHub](https://github.com/mamacneil/NutrientFishbase). In the plots below we refer to the Recommended Daily Intake of a woman between 31 and 50 years old [@Trumbo2002] to estimate the overall nutritional value.

```{r, echo=FALSE, warning=FALSE, eval=TRUE, message=FALSE, fig.height=9, fig.width=8.5}
nutrient_table %>%
  dplyr::rename(catch_taxon = .data$interagency_code) %>%
  dplyr::left_join(catch_types, by = "catch_taxon") %>%
  dplyr::select(-c(.data$`Taxonomic rank (family)`, .data$catch_taxon)) %>%
  dplyr::select(.data$`Common name`, tidyselect::everything()) %>%
  dplyr::mutate(dplyr::across(c(.data$Selenium_mu:.data$Vitamin_A_mu), ~ .x * 100)) %>%
  dplyr::transmute(
    taxa_group = .data$`Common name`,
    Selenium = .data$Selenium_mu / RDI_Selenium * 100,
    Zinc = .data$Zinc_mu / RDI_Zinc * 100,
    Calcium = .data$Calcium_mu / RDI_Calcium * 100,
    Iron = .data$Iron_mu / RDI_Iron * 100,
    "Vitamin A" = .data$Vitamin_A_mu / RDI_VitaminA * 100,
    "Omega-3" = .data$Omega_3_mu / RDI_Omega * 100,
    Protein = .data$Protein_mu / RDI_Protein * 100
  ) %>%
  tidyr::pivot_longer(-.data$taxa_group) %>%
  dplyr::mutate(name = stringr::str_replace(.data$name, pattern = "_sc", "")) %>%
  dplyr::filter(!is.na(.data$value)) %>%
  dplyr::mutate(name = factor(name, levels = rev(c("Selenium", "Protein", "Omega-3", "Zinc", "Calcium", "Iron", "Vitamin A")), ordered = TRUE)) %>%
  # dplyr::group_by(taxa_group) %>%
  # dplyr::mutate(tot_value = sum(value)) %>%
  # dplyr::arrange(dplyr::desc(tot_value)) %>%
  # dplyr::ungroup() %>%
  # dplyr::top_n(n = 10*7) %>%
  ggplot(aes(x = taxa_group, y = value, fill = name)) +
  geom_col(mapping = aes(x = reorder(taxa_group, value), y = value, fill = name)) +
  scale_fill_viridis_d(direction = -1) +
  # scale_fill_manual(values=rev(c("#E7A977","#BED8D4","#2081C3","#B3BFB8","#BF211E","#297045","#B3679B")))+
  theme_minimal(14) +
  coord_flip() +
  labs(
    x = "",
    y = "RDI (%) from 100g portion",
    fill = "",
    title = "Fish groups nutritional contribution",
    subtitle = "Median contribution of fish groups to the Recommended\nNutrient Intakes (%) for the seven nutrients considered."
  ) +
  theme(
    text = element_text(family = "Helvetica"),
    plot.title = element_text(size = 18),
    plot.subtitle = element_text(size = 13, color = "darkslategrey")
  )
```

```{r, echo=FALSE, warning=FALSE, eval=TRUE, message=FALSE, fig.height=5, fig.width=6}
dplyr::left_join(catch, trips, by = "trip_id") %>%
  dplyr::filter(individuals > 0) %>%
  dplyr::select(trip_id, landing_date, reporting_region, catch_taxon, weight:Vitamin_A_mu) %>%
  dplyr::left_join(catch_types, by = "catch_taxon") %>%
  dplyr::select(-`Taxonomic rank (family)`) %>%
  dplyr::transmute(
    Selenium = .data$Selenium_mu / RDI_Selenium,
    Zinc = .data$Zinc_mu / RDI_Zinc,
    Calcium = .data$Calcium_mu / RDI_Calcium,
    Iron = .data$Iron_mu / RDI_Iron,
    "Vitamin A" = .data$Vitamin_A_mu / RDI_VitaminA,
    "Omega-3" = .data$Omega_3_mu / RDI_Omega,
    Protein = .data$Protein_mu / RDI_Protein
  ) %>%
  na.omit() %>%
  tidyr::pivot_longer(tidyselect::everything()) %>%
  dplyr::mutate(name = stringr::str_replace(.data$name, pattern = "_sc", "")) %>%
  dplyr::group_by(name) %>%
  dplyr::summarise(
    mean = mean(value, na.rm = TRUE),
    sd = sd(value, na.rm = TRUE),
    n = dplyr::n(),
    q95 = quantile(value, 0.95, na.rm = TRUE),
    q75 = quantile(value, 3 / 4, na.rm = TRUE),
    q25 = quantile(value, 1 / 4, na.rm = TRUE),
    q5 = quantile(value, 0.05, na.rm = TRUE)
  ) %>%
  ggplot(aes(x = mean, y = reorder(name, mean))) +
  ungeviz::stat_confidence_density(
    aes(moe = q95 - mean, fill = stat(ndensity)),
    height = 0.7,
    confidence = 0.95,
    alpha = NA
  ) +
  geom_segment(
    aes(
      x = mean, xend = mean,
      y = as.integer(reorder(name, mean)) - 0.35,
      yend = as.integer(reorder(name, mean)) + 0.35
    ),
    size = 2, color = "#D55E00"
  ) +
  scale_fill_gradient(low = "#81A7D600", high = "#2d3f68") +
  scale_x_continuous(
    name = "Recommended Daily Intake (%)",
    limits = c(0, 200),
    expand = c(0, 0)
  ) +
  scale_y_discrete(name = NULL) +
  theme_minimal(12) +
  theme(
    plot.subtitle = element_text(size = 13, color = "darkslategrey")
  ) +
  labs(
    x = "",
    y = "RDI (%)",
    fill = "",
    title = "Catches' nutritional properties",
    subtitle = "Average nutritional properties of Timor catches relative to the Recommended\nDaily Intake (%). The orange line represent the mean, shaded areas represent\nthe limits of the 95% confidence interval with dark shades indicating high density\nin the distribution."
  ) +
  theme(
    text = element_text(family = "Helvetica"),
    plot.title = element_text(size = 17),
    plot.subtitle = element_text(size = 10, color = "darkslategrey")
  )
```

```{r, echo=FALSE, warning=FALSE, eval=TRUE, message=FALSE, fig.height=10, fig.width=8}
dplyr::left_join(catch, trips, by = "trip_id") %>%
  dplyr::filter(individuals > 0) %>%
  dplyr::select(trip_id, landing_date, reporting_region, catch_taxon, weight:Vitamin_A_mu) %>%
  dplyr::left_join(catch_types, by = "catch_taxon") %>%
  dplyr::select(-`Taxonomic rank (family)`) %>%
  dplyr::transmute(
    landing_date = .data$landing_date,
    month_date = lubridate::floor_date(.data$landing_date, unit = "month"),
    Selenium = .data$Selenium_mu / RDI_Selenium,
    Zinc = .data$Zinc_mu / RDI_Zinc,
    Calcium = .data$Calcium_mu / RDI_Calcium,
    Iron = .data$Iron_mu / RDI_Iron,
    "Vitamin A" = .data$Vitamin_A_mu / RDI_VitaminA,
    "Omega-3" = .data$Omega_3_mu / RDI_Omega,
    Protein = .data$Protein_mu / RDI_Protein
  ) %>%
  dplyr::group_by(month_date) %>%
  dplyr::select(-landing_date) %>%
  dplyr::summarise_all(sum, na.rm = TRUE) %>%
  tidyr::pivot_longer(-.data$month_date) %>%
  dplyr::mutate(name = stringr::str_replace(.data$name, pattern = "_sc", "")) %>%
  dplyr::mutate(name = factor(name, levels = c("Selenium", "Protein", "Omega-3", "Zinc", "Calcium", "Iron", "Vitamin A"), ordered = TRUE)) %>%
  ggplot(aes(x = month_date, y = value)) +
  facet_grid(name ~ ., scales = "free_y") +
  geom_line(aes(color = name), show.legend = FALSE) +
  geom_area(aes(fill = name), alpha = 0.5) +
  scale_x_date(
    date_breaks = "3 month", minor_breaks = NULL, labels = label_date,
    limits = c(as.Date("2019-01-01"), Sys.Date() - 31)
  ) +
  scale_y_continuous(labels = scales::comma, limits = c(0, NA)) +
  scale_color_viridis_d(direction = 1) +
  scale_fill_viridis_d(direction = 1) +
  theme_minimal(17) +
  theme(
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    text = element_text(family = "Helvetica"),
    legend.position = "bottom",
    plot.title = element_text(size = 18),
    plot.subtitle = element_text(size = 13, color = "darkslategrey")
  ) +
  labs(
    x = "Date",
    y = "RDI covered (number of people)",
    color = "",
    fill = "",
    title = "Nutrients coverage",
    subtitle = "Monthly number of people feed by small-scale fisheries in Timor according to\nthe Recommended Daily Intake for the seven nutrients considered. Note the\nincrease in vitamin A coverage over time."
  )
```

```{r, echo=FALSE, warning=FALSE, eval=TRUE, message=FALSE, fig.height=10, fig.width=8}
dplyr::left_join(catch, trips, by = "trip_id") %>%
  dplyr::filter(individuals > 0) %>%
  dplyr::select(trip_id, landing_date, reporting_region, catch_taxon, weight:Vitamin_A_mu) %>%
  dplyr::left_join(catch_types, by = "catch_taxon") %>%
  dplyr::select(-c(trip_id:weight, `Taxonomic rank (family)`)) %>%
  dplyr::rename(
    "Vitamin A_mu" = .data$Vitamin_A_mu,
    "Omega-3_mu" = .data$Omega_3_mu
  ) %>%
  tidyr::pivot_longer(-`Common name`) %>%
  dplyr::group_by(`Common name`, name) %>%
  dplyr::summarise(value = sum(value, na.rm = TRUE)) %>%
  dplyr::group_by(name) %>%
  dplyr::top_n(n = 10, wt = value) %>%
  dplyr::mutate(name = stringr::str_replace(.data$name, pattern = "_mu", "")) %>%
  dplyr::mutate(name = factor(name, levels = c("Selenium", "Protein", "Omega-3", "Zinc", "Calcium", "Iron", "Vitamin A"), ordered = TRUE)) %>%
  dplyr::mutate(
    name = as.factor(name),
    `Common name` = tidytext::reorder_within(`Common name`, value, name)
  ) %>%
  ggplot(aes(`Common name`, value / 1000, fill = name)) +
  facet_wrap(. ~ name, scales = "free", ncol = 2) +
  geom_col() +
  coord_flip() +
  tidytext::scale_x_reordered() +
  theme_minimal(13) +
  scale_fill_viridis_d() +
  labs(
    x = "",
    y = "Kg"
  ) +
  theme(
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    text = element_text(family = "Helvetica"),
    legend.position = "bottom",
    plot.title = element_text(size = 18),
    plot.subtitle = element_text(size = 12.5, color = "darkslategrey")
  ) +
  labs(
    x = "",
    y = "Kg",
    color = "",
    fill = "",
    title = "Fish groups nutrients' stock",
    subtitle = "Contribution of fish groups to nutrients' aggregated stock. Sardines\nrepresent the main source of almost all the nutrients except for calcium\nand vitamin A. These two nutrients are mostly provided by mackerels and\nby the group formed by snappers, long toms, and fusiliers respectively."
  )
```

```{r, echo=FALSE, warning=FALSE, eval=TRUE, message=FALSE, fig.height=6, fig.width=7}
dplyr::left_join(catch, trips, by = "trip_id") %>%
  dplyr::filter(individuals > 0 & !is.na(habitat)) %>%
  dplyr::select(habitat, weight:Vitamin_A_mu) %>%
  dplyr::mutate(dplyr::across(c(.data$Selenium_mu:.data$Vitamin_A_mu), ~ (.x / weight) * 100)) %>%
  dplyr::group_by(habitat) %>%
  dplyr::summarise_all(mean, na.rm = TRUE) %>%
  dplyr::transmute(
    habitat = .data$habitat,
    Selenium = .data$Selenium_mu / RDI_Selenium * 100,
    Zinc = .data$Zinc_mu / RDI_Zinc * 100,
    Calcium = .data$Calcium_mu / RDI_Calcium * 100,
    Iron = .data$Iron_mu / RDI_Iron * 100,
    "Vitamin A" = .data$Vitamin_A_mu / RDI_VitaminA * 100,
    "Omega-3" = .data$Omega_3_mu / RDI_Omega * 100,
    Protein = .data$Protein_mu / RDI_Protein * 100
  ) %>%
  tidyr::pivot_longer(-.data$habitat) %>%
  dplyr::filter(!is.na(.data$value)) %>%
  dplyr::mutate(name = factor(name, levels = rev(c("Selenium", "Protein", "Omega-3", "Zinc", "Calcium", "Iron", "Vitamin A")), ordered = TRUE)) %>%
  ggplot(aes(x = habitat, y = value, fill = name)) +
  geom_col(mapping = aes(x = reorder(habitat, value), y = value, fill = name)) +
  scale_fill_viridis_d(direction = -1) +
  theme_minimal(12) +
  coord_flip() +
  labs(
    x = "",
    y = "RDI (%) from 100g portion",
    fill = "",
    title = "Nutrients distribution by habitat",
    subtitle = "Distribution of nutrients' concentration relative to the\nRecommended Daily Intake (%) of 100g of catch\nin each habitat monitored in Timor."
  ) +
  theme(
    text = element_text(family = "Helvetica"),
    plot.title = element_text(size = 16),
    plot.subtitle = element_text(size = 12, color = "darkslategrey")
  )
```

\pagebreak

# About Peskas

Peskas is the official fisheries national monitoring system of Timor-Leste and represents one of the most sophisticated data collection systems for small-scale fisheries in the world.

Peskas' platform collects real-time information directly from fishermen's activity via a system of digital surveys developed in [KoBo toolbox](http://www.kobotoolbox.org/). In addition, Peskas uses the technology provided by [Pelagic Data System](https://www.pelagicdata.com/) to record vessel movements via solar-powered tracking devices).

The data and the information collected is subjected to an elaborate processing and cleaning through an open-source code pipeline on [GitHub](https://github.com/WorldFishCenter/peskas.timor.data.pipeline), and provide important data in the hands of fisheries officers, researchers and local stakeholders and enables them to better understand the contribution of fish and fisheries to local livelihoods and food security.

Information about the process and user-centred design of the Peskas pipeline and initial analytics, and its application in fisheries research & management can be found in the following publications:

-   [PeskAAS: A near real-time monitoring system for small-scale fisheries in Timor-Leste](https://www.fao.org/documents/card/en/c/cb2030en). In A. Tilley & M. B. Roscher (Eds.), Information and communication technologies for small-scale fisheries (ICT4SSF) - A handbook for fisheries stakeholders. In support of the implementation of the Voluntary Guidelines for Securing Sustainable Small-Scale Fisheries in the Context of Food Security and Poverty Eradication (pp. 11--18). FAO; WorldFish.
-   [PeskAAS: A near-real-time, open-source monitoring and analytics system for small-scale fisheries](https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0234760). PloS One, 15(11), e0234760.
-   [Nearshore Fish Aggregating Devices Show Positive Outcomes for Sustainable Fisheries Development in Timor-Leste](https://www.frontiersin.org/articles/10.3389/fmars.2019.00487/full). Frontiers in Marine Science, 6, 487.

\pagebreak

# References
